Incremental Forward Reasoning for White-Box~Proof~Search

### 2025-02-17 paper.tex
Add some intro TODOs

Typical rules would be the $∧$-introduction lemma $A → B → A ∧ B$, which, when applied backwards, reduces a goal $Γ ⊢ A ∧ B$ to subgoals $Γ ⊢ A$ and $Γ ⊢ B$; or left $∨$-introduction, which reduces $Γ ⊢ A ∨ B$ to $Γ ⊢ A$.
Such \emph{backward rules} are the most common rule type, but most search tactics allow users to use any tactic as a rule.
These rule tactics can output arbitrary subgoals, subject only to the condition that proofs of the returned subgoals can be assembled into a proof of the goal on which the rule was run.

ACL2, PVS and Aesop provide special support for \emph{forward rules}.
Given, for example, the transitivity lemma $\All{x~y~z}{x < y → y < z → x < z}$, a forward rule run on the goal $h₁ : a < b,\, h₂ : b < c ⊢ A$ produces the single subgoal $h₁ : a < b,\, h₂ : b < c,\, h₃ : a < c ⊢ A$.
Hence forward rules can be used to establish additional facts that may be relevant for other rules.
For example, the Aeneas project (TODO ref) uses Aesop's forward rules \jcom{(ensure that this is accurate)} in its proof automation to establish facts that are later used by an arithmetic decision procedure.

>>>>

Typical rules would be the $∧$-introduction lemma $A → B → A ∧ B$, which, when applied backwards, reduces a goal $Γ ⊢ A ∧ B$ to subgoals $Γ ⊢ A$ and $Γ ⊢ B$; or left $∨$-introduction, which reduces $Γ ⊢ A ∨ B$ to $Γ ⊢ A$.
Such \emph{backward rules} are the most common rule type, but most search tactics allow users to use any tactic as a rule.
These rule tactics can output arbitrary subgoals, subject only to the condition that proofs of the returned subgoals can be assembled into a proof of the goal on which the rule was run.
\jcom{The framing here is wrong: we want to talk about non-forward rules that mess with the context, e.g. case splitting.}

ACL2, PVS and Aesop provide special support for \emph{forward rules}.
Given, for example, the transitivity lemma $\All{x~y~z}{x < y → y < z → x < z}$, a forward rule run on the goal $h₁ : a < b,\, h₂ : b < c ⊢ A$ produces the single subgoal $h₁ : a < b,\, h₂ : b < c,\, h₃ : a < c ⊢ A$.
Hence forward rules can be used to establish additional facts that may be relevant for other rules.
For example, the Aeneas project (TODO ref) uses Aesop's forward rules \jcom{ensure that this is accurate} in its proof automation to establish facts that are later used by an arithmetic decision procedure.
